---
title: "Progress Report 2_Data"
author: "Zihan Gao"
data: "Nov 11, 2025"
format: gfm
---

## Progress report 2
## Zihan Gao
## Nov 11, 2025

### Notes at the beginning
I wasn’t able to finish the data collection process by noon on November 11. I will list one example and complete the related questions first, then apply the same procedure to the other four dialects.

### Data Type
- Existing, but I have added/changed a lot.
- I also want to note that I asked ChatGPT for a lot of help because I really had no idea how to extract data from a dynamic website. I did try using the textbook, including the code, packages, and functions mentioned there, but most of the current code was written by ChatGPT. There are still two lines that I don’t fully understand.

### My study
#### Title
Dialects reduce attractiveness?: A Study of Language Attitudes and Stereotypes toward Chinese Dialects on Social Media

### Update of code

In the previous progress report, I managed to extract the titles of videos on the first page. During the past week, I worked on figuring out how to turn pages and extract the number of views for each video. However, I wasn’t able to make it work. Because the website is dynamic, the code always returned `character(0)`. Therefore, I tried sorting the results by view count and extracting only the titles from the first page. With help from ChatGPT, this approach worked. The code is shown below.

#### Step 1 extract the titles, name of uploaders, and the date when the video was uploaded

```{r}
# load packages
library(rvest)
library(chromote)
library(dplyr)
library(writexl)
```

```{r}
# create Chromote session
b <- ChromoteSession$new()

# name keyword (Cantonese), and rank by number of views
keyword <- "粤语"
url <- paste0(
  "https://search.bilibili.com/all?keyword=",
  URLencode(keyword),
  "&order=click"  # rank by views
)

# open the page
b$Page$navigate(url)

# wait time
Sys.sleep(6)

# get the HTML
html_text <- b$Runtime$evaluate("document.documentElement.outerHTML")$result$value
html <- read_html(html_text)

# I actually don't understand this step below
cards <- html_elements(html, ".bili-video-card")

# extract the keyword
titles <- cards |> html_element(".bili-video-card__info--tit") |> html_text2()
ups    <- cards |> html_element(".bili-video-card__info--owner") |> html_text2()
dates  <- cards |> html_element(".bili-video-card__info--date") |> html_text2()

# I don't understand the code below.
# It seems to give a back up option.
if (length(ups) == 0) {
  ups <- cards |> html_element(".bili-video-card__info--author") |> html_text2()
}
if (length(dates) == 0) {
  dates <- cards |> html_element(".bili-video-card__info--pubdate") |> html_text2()
}

# build the dataframe
df <- data.frame(
  title = titles,
  up    = ups,
  date  = dates,
  stringsAsFactors = FALSE
)

# output
write_xlsx(df, path = "Cantonese_videos.xlsx")

# close the window
b$close()
```


#### Step 2 input the view count (manually?)
I found the view count in the HTML code, but I wasn’t able to extract it. I’ll keep working on it a bit more. It should be extractable.

I actually entered the view counts manually, but I accidentally ran the above code again and the file was overwritten 😭. I’ll work on extracting it from the HTML language instead of entering manually. 

#### Step 3 code the video type
I had also coded different videos based on their content (e.g., music, humor, mocking, etc.), but unfortunately, I lost that data as well because the file was overwritten.

#### Step 4 decide the dialects
Another step I completed was deciding which dialects to focus on. Instead of using linguistically defined Chinese dialects or varieties, I decided to use provinces. I found data on the GDP of each province and ranked them from highest to lowest. I will focus on the top five provinces.

### Step 5 repeat the previous steps
I have tried another code and was able to extract the titles of the 42 most frequently viewed videos for all five dialects. But this morning, I updated the code to include the uploader’s name and the publication date for Cantonese. I haven't had a chance to update the code for the other dialects because I was manualing entering view counts.


